Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2024-03-04 Edith Zemanick/Sweat Test/sweat_test_analysis.Rmd
paths

```{r warning=FALSE}
set.seed(1017)
# K means
km_df <- df %>%
  select(Diagnosis, `Na/Cl Ratio`) %>%
  drop_na()
km <- kmeans(km_df[, c("Na/Cl Ratio")], centers = 3)
km_df$Cluster <- factor(km$cluster,
  levels = 1:3,
  labels = c("Low","Medium","High")
)
centers <- data.frame(km$centers)
centers$Cluster <- rownames(km$centers)
centers$Cluster <- factor(centers$Cluster,
  levels = 1:3,
  labels = c("Low","Medium","High")
)
rownames(centers) <- NULL
centers <- centers %>% column_to_rownames("Cluster")
kable(centers, caption = "K-means centers", row.names = T)
kable(as.data.frame.matrix(table(km_df$Cluster, km_df$Diagnosis)), row.names = T)
```

>>>>

```{r warning=FALSE}
set.seed(1017)
# K means
km_df <- df %>%
  select(Diagnosis, `Na/Cl Ratio`) %>%
  drop_na()
km <- kmeans(km_df[, c("Na/Cl Ratio")], centers = 3)
km_df$Cluster <- factor(km$cluster,
  levels = 1:3,
  labels = c("Low", "Medium", "High")
)
centers <- data.frame(km$centers)
centers$Cluster <- rownames(km$centers)
centers$Cluster <- factor(centers$Cluster,
  levels = 1:3,
  labels = c("Low", "Medium", "High")
)
rownames(centers) <- NULL
centers <- centers %>% column_to_rownames("Cluster")
kable(centers, caption = "K-means centers", row.names = T)
kable(as.data.frame.matrix(table(km_df$Cluster, km_df$Diagnosis)), row.names = T)
```
